---
title: "CLT-based Inference"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```


# Packages and Data

```{r packages}
library(tidyverse)
library(infer)
```

The data in `songs` contain the length in minutes of the 3,000 songs on a
person's phone (consider this as the entire population).

```{r load_data}
songs <- read_csv("data/songs.csv")
```

# Exercises

## Exercise 1

What is the population mean and standard deviation of song length?

## Exercise 2

What is the probability that a randomly selected song is longer than 5
minutes long?

## Exercise 3

Set the seed to `53251` and take a random sample of 100 songs. 

Construct a 95% confidence interval for the mean song length using your 
random sample. Did your interval contain the true population mean?

## Exercise 4

On a 6 hour drive, what is the probability that a randomly selected playlist
of 100 songs lasts the length of the trip?

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.
